Occultation Light Curves in Reflected Light

### 2020-04-01 tex/ms.tex
tweaks

%
\section{The Problem}
\label{sec:the-problem}
%
As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
a spherical body whose surface intensity is described by the spherical harmonic
coefficient vector $\mathbf{y}$ as
%
\begin{align}
    \label{eq:sTARRy}
    f = \bvec{s}^\top \bvec{A} \bvec{R}' \bvec{R} \bvec{y}
    \quad,
\end{align}
%
where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices
\citep[\S3.3 of][]{Luger2019},
$\bvec{A}$ is the change-of-basis matrix from spherical harmonics
to a basis $\tilde{\bvec{g}}$ \citep[Equation B13 in][]{Luger2019},
and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
of the basis functions in $\tilde{\bvec{g}}$ over
the projected visible disk of the body (which may be partially occulted by
another spherical body).
%
The basis $\tilde{\bvec{g}}$ is called the \emph{Green's basis}; its name
stems from the fact that its components have a structure that makes integration
by Green's theorem convenient. Its components were defined in
Equation~11 of \citet{Luger2019b}:
%
\begin{proof}{bg}
    \tilde{g}_{l,m} &=
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \, \mathrm{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \mathrm{otherwise}
        \quad,
    \end{dcases}
    \label{eq:bg}
\end{proof}
%
where $x$ and $y$ are the Cartesian components on the surface
of the projected
disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
%
\begin{align}
    \mu & = l - m
    \nonumber     \\
    \nu & = l + m
    \quad.
\end{align}
%
The vector $\tilde{\bvec{g}}$ is structured such that
the component at index $n$ is $\tilde{g}_{l,m}$ with
\begin{align}
    \label{eq:lm}
    l & = \floor*{\sqrt{n}} \nonumber \\
    m & = n - l^2 - l
    \quad.
\end{align}
\xxx{The rotation matrices do the following...}
For more information on all of these terms, the reader is referred to
\citet{Luger2019}.

@@

Our task is to compute the solution vector for this
configuration, which we will denote $\bvec{s}^\top_0$.  When no occultor
is present (as in this case), it is
more convenient to perform the integration in the \emph{polynomial basis}
$\tilde{\bvec{p}}$ \citep[Equation 7 in][]{Luger2019}:
%
\begin{align}
    \tilde{p}_{l,m}(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \mathrm{otherwise} \quad,
    \end{dcases}
\end{align}
%
where \xxx{we unroll p as before...}
The solution vector is then given by
%
\begin{align}
    \label{eq:sTref}
    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R} \bvec{A}^{-1}
    \quad,
\end{align}
%
where $\bvec{r}^\top$ is the solution vector in the polynomial basis,
$\bvec{A_1}$ is the change-of-basis matrix between the polynomial basis
and the spherical harmonic basis, $\bvec{R}$ is a spherical harmonic rotation
matrix, and $\bvec{A}$ is the change-of basis matrix between the spherical
harmonic basis and the Green's basis.
\xxx{In words, the equation above reads...}

\xxx{...} In this frame, the body sits at the origin and is illuminated by a point
source in the
$y-z$ plane at coordinates $(0, y_s, z_s)$. It is straightforward to show
that the illumination at a point $(x, y)$ on the projected disk is
given by
%
\begin{proof}{illum}
    \Psi(b; x, y) & =
    \begin{dcases}
        b_cy - bz(x, y) &
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
        y \geq b \sqrt{1 - x^2}
        \\
        0               &
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
        \mathrm{otherwise}
    \end{dcases}
    \quad ,
    \label{eq:illum}
\end{proof}
%
where $b_c = \sqrt{1 - b^2}$.
%
\xxx{The solution vector may then be computed as...}
%
\begin{align}
    \label{eq:rT}
    r_{n(\mu,\nu)} & =
    \int_{-1}^{1}
    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
    \tilde{p}_{n(\mu,\nu)}(x, y)
    \Psi(b; x, y)
    \ \dd y \ \dd x
    \quad.
\end{align}
%
Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
trigonometric and algebraic functions of $b$:
%
\begin{proof}{rT}
    \label{eq:rTsoln}
    r_{n(\mu,\nu)} & =
    \begin{cases}
        \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
        J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
        b I_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
        %
         &
        %
        \qquad
        \mu, \nu \ \mathrm{even}
        %
        \\[1em]
        %
        b_c
        I_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
        %
        \\[0.5em]
        \qquad
        %
        - \frac{b}{2} \bigg\{
        \left(1 - b^{\frac{\nu + 1}{2}}\right)
        \left(
        J_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
        J_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
        \right)
        \\[0.5em]
        \qquad\qquad
        -
        \left(1 - b^{\frac{\nu + 5}{2}}\right)
        J_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
        \bigg\}
        %
         &
        %
        \qquad
        \mathrm{otherwise}
        %
    \end{cases}
\end{proof}
%
where
%
\begin{proof}{rT}
    \label{eq:IJK}
    I_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
    \nonumber \\
    %
    J_{i,j} &=
    \frac{
        \Gamma\left(\frac{i + 1}{2}\right)
        \Gamma\left(\frac{j + 1}{2}\right)
    }
    {
        \Gamma\left(\frac{i + j + 4}{2}\right)
    }
    %
    \nonumber \\
    %
    K_{i,j} &=
    \frac{
        \Gamma\left(\frac{i + 1}{2}\right)
        \Gamma\left(\frac{j + 4}{2}\right)
    }
    {
        \Gamma\left(\frac{i + j + 5}{2}\right)
    }
    \quad.
\end{proof}
%
Given initial conditions
%
\\[1em]
\begin{minipage}{.33\linewidth}
    \begin{proof}{rT}
        I_{0}(b) &= \frac{\arccos(b) - bb_c}{2}
        %
        \nonumber \\
        %
        I_{1}(b) &= \frac{b_c^3}{3}
        %
        \nonumber
    \end{proof}
\end{minipage}%
\begin{minipage}{.32\linewidth}
    \begin{proof}{rT}
        J_{0,0} &= \pi
        %
        \nonumber \\
        %
        J_{0,1} &= \frac{4}{3}
        %
        \nonumber
    \end{proof}
\end{minipage}%
\begin{minipage}{.33\linewidth}
    \begin{proof}{rT}
        \label{eq:IJK0}
        K_{0,0} &= \frac{4}{3}
        %
        \nonumber \\
        K_{0,1} &= \frac{3\pi}{8}
    \end{proof}
\end{minipage}
\\[1em]
%
we may compute all higher order terms from the recurrence relations
%
\begin{proof}{rT}
    \label{eq:IJKrec}
    I_{j}(b) &= \frac{b^n b_c^3 + (j - 1) I_{j - 2}(b)}{j + 2}
    %
    \nonumber \\
    %
    J_{0,j} &= \left(\frac{j - 1}{j + 2}\right) J_{0,j-2}
    %
    \nonumber \\
    %
    K_{0,j} &= \left(\frac{j + 2}{j + 3}\right) K_{0,j-2}
    %
    \nonumber \\
    %
    J_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) J_{i-2,j}
    %
    \nonumber \\
    %
    K_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) K_{i-2,j}
    \quad.
\end{proof}
%

>>>>

%
\section{The Problem}
\label{sec:the-problem}
%
As in \citet{Luger2019}, we compute the instantaneous visible flux $f$ from
a spherical body whose surface intensity is described by the spherical harmonic
coefficient vector $\mathbf{y}$ in some static frame $\mathcal{F}$ as
%
\begin{align}
    \label{eq:sTARRy}
    f = \bvec{s}^\top \bvec{A} \bvec{R}' \bvec{R} \bvec{y}
    \quad,
\end{align}
%
where $\bvec{R}$ and $\bvec{R}'$ are spherical harmonic rotation matrices
\citep[\S3.3 of][]{Luger2019},
$\bvec{A}$ is the change-of-basis matrix from spherical harmonics
to a basis $\tilde{\bvec{g}}$ \citep[Equation B13 in][]{Luger2019},
and $\bvec{s}^\top$ is the \emph{solution vector}, the integral of each
of the basis functions in $\tilde{\bvec{g}}$ over
the projected visible disk of the body (which may be partially occulted by
another spherical body).
%
The basis $\tilde{\bvec{g}}$ is called the \emph{Green's basis}; its name
stems from the fact that its components have a structure that makes integration
by Green's theorem convenient. Its components were defined in
Equation~11 of \citet{Luger2019b}:
%
\begin{proof}{bg}
    \tilde{g}_{l,m} &=
    \begin{dcases}
        %
        \frac{\mu+2}{2}x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
         & \qquad \mu = \nu = 1
        \\[1em]
        %
        3x^{l-2}yz(x, y)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \frac{\mu + \nu}{2} \, \mathrm{even}
        \\[1em]
        %
        z(x, y)
        \bigg(
        -x^{l-3} + x^{l-1} + 4x^{l-3}y^2
        \bigg)
         & \qquad \nu \, \mathrm{odd}, \,
        \mu = 1, \,
        \, \mathrm{odd}
        \\[1em]
        %
        z(x, y)
        \bigg(
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu-1}{2}
        \ - \
        \frac{\mu-3}{2} x^\frac{\mu-5}{2} y^\frac{\nu+3}{2}
        \\
        \qquad\qquad \ - \
        \frac{\mu+3}{2} x^\frac{\mu-1}{2} y^\frac{\nu-1}{2}
        \bigg)
         & \qquad \mathrm{otherwise}
        \quad,
    \end{dcases}
    \label{eq:bg}
\end{proof}
%
where $x$ and $y$ are the Cartesian coordinates on the surface
of the projected
disk of the body, with $z(x, y) = \sqrt{1 - x^2 - y^2}$, and
%
\begin{align}
    \label{eq:munu}
    \mu & = l - m
    \nonumber     \\
    \nu & = l + m
    \quad.
\end{align}
%
The vector $\tilde{\bvec{g}}$ is ordered such that
the component at index $n$ is $\tilde{g}_{l,m}$, with
\begin{align}
    \label{eq:lm}
    l & = \floor*{\sqrt{n}} \nonumber \\
    m & = n - l^2 - l
    \quad.
\end{align}
Finally, the rotation matrix $\bvec{R} = \bvec{R}(i, \lambda, \theta)$
rotates the body to the correct orientation on the sky given its
inclination $i$, obliquity $\lambda$, and rotational phase $\theta$,
while $\bvec{R}'$ rotates the body on the plane
of the sky into the frame $\mathcal{F}'$ in which the integration is
actually performed, with the occultor along the $+y$-axis.
For more information on all of these terms, the reader is referred to
\citet{Luger2019}.

@@

Our task is to compute the solution vector for this
configuration, which we will denote $\bvec{s}^\top_0$.
Since in this case there is no occultor, it is
more convenient to perform the integration in a frame $\mathcal{F}''$ where the
semi-major axis of the terminator is aligned with the $x$-axis
(see Figure~\ref{fig:illum}); let us denote the matrix that rotates us
from $\mathcal{F}'$ to $\mathcal{F}''$ as $\bvec{R}''$.
It is also far easier to perform the integration
in the \emph{polynomial basis} $\tilde{\bvec{p}}$
\citep[Equation 7 in][]{Luger2019}:
%
\begin{align}
    \tilde{p}_{l,m}(x, y) & =
    \begin{dcases}
        x^\frac{\mu}{2} y^\frac{\nu}{2}
         & \qquad \mu, \nu \, \mathrm{even}
        \\[1em]
        x^\frac{\mu-1}{2} y^\frac{\nu-1}{2} z(x, y)
         & \qquad \mathrm{otherwise} \quad,
    \end{dcases}
\end{align}
%
where $\tilde{\bvec{p}}$ is again ordered such that the component at
index $n$ is $\tilde{p}_{l,m}$, with $l$ and $m$ given by
Equation~(\ref{eq:lm}).
Now, if $\bvec{r}^\top$ is the solution to the surface integrals in the
polynomial basis in $\mathcal{F}''$,
we may compute the desired solution vector in the Green's basis from
%
\begin{align}
    \label{eq:sTref}
    \bvec{s}^\top_0 & = \bvec{r}^\top \bvec{A_1} \bvec{R}'' \bvec{A}^{-1}
    \quad,
\end{align}
%
where $\bvec{A_1}$ \citep[Equation B11 in][]{Luger2019}
transforms the solution into the spherical harmonic basis so it can
be rotated out of the integration frame $\mathcal{F}''$ via $\bvec{R}''$, and
$\bvec{A}^{-1}$ \citep[Equation B13 in][]{Luger2019} transforms the
result into the Green's basis (in which $\bvec{s}^\top$ is defined).

Our task is thus to compute $\bvec{r}^\top$.
In frame $\mathcal{F}''$, the body sits at the origin and is
illuminated by a point source in the
$y-z$ plane at coordinates $(0, y_s, z_s)$ as in Figure~\ref{fig:illum}.
The day/night terminator is a half-ellipse whose semi-major axis
is unity and is aligned with the $x$-axis. The semi-minor axis is given
by $b = -\nicefrac{z_s}{\sqrt{y_s^2 + z_s^2}}$, where $b > 0$ corresponds to
a half-ellipse that is concave down and $b < 0$ to one that is concave up.
It is straightforward to show
that the illumination at a point $(x, y)$ on the projected disk is
given by
%
\begin{proof}{illum}
    \Psi(b; x, y) & =
    \begin{dcases}
        b_cy - bz(x, y) &
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
        y \geq b \sqrt{1 - x^2}
        \\
        0               &
        \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
        \mathrm{otherwise}
    \end{dcases}
    \quad ,
    \label{eq:illum}
\end{proof}
%
where $b_c = \sqrt{1 - b^2}$.
%
The elements of the solution vector may then be computed from
%
\begin{align}
    \label{eq:rT}
    r_{l, m}(b) & =
    \int_{-1}^{1}
    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
    \tilde{p}_{n(\mu,\nu)}(x, y)
    \Psi(b; x, y)
    \ \dd y \ \dd x
    \quad.
\end{align}
%
This is the integral of the illumination-weighted intensity of each
term in the polynomial basis over the projected visible dayside of the
body.
%
Equation~(\ref{eq:rT}) may be solved analytically in terms of purely
trigonometric and algebraic functions of $b$:
%
\begin{proof}{rT}
    \label{eq:rTsoln}
    r_{l, m}(b) & =
    \begin{cases}
        \frac{b_c\left(1 - b^{\frac{\nu + 4}{2}}\right)}{2}
        J_{\frac{\mu}{2}, \frac{\nu + 2}{2}} -
        b I_\frac{\nu}{2}(b) K_{\frac{\mu}{2}, \frac{\nu}{2}}
        %
         &
        %
        \qquad
        \mu, \nu \ \mathrm{even}
        %
        \\[1em]
        %
        b_c
        I_{\frac{\nu + 1}{2}}(b) K_{\frac{\mu - 1}{2}, \frac{\nu + 1}{2}}
        %
        \\[0.5em]
        \qquad
        %
        - \frac{b}{2} \bigg\{
        \left(1 - b^{\frac{\nu + 1}{2}}\right)
        \left(
        J_{\frac{\mu - 1}{2}, \frac{\nu - 1}{2}} -
        J_{\frac{\mu + 3}{2}, \frac{\nu - 1}{2}}
        \right)
        \\[0.5em]
        \qquad\qquad
        -
        \left(1 - b^{\frac{\nu + 5}{2}}\right)
        J_{\frac{\mu - 1}{2}, \frac{\nu + 3}{2}}
        \bigg\}
        %
         &
        %
        \qquad
        \mathrm{otherwise}
        %
    \end{cases}
\end{proof}
%
where
%
\begin{proof}{rT}
    \label{eq:IJK}
    I_{j}(b) &= \int_b^1 a^j \sqrt{1 - a^2} \dd a
    \nonumber \\
    %
    J_{i,j} &=
    \frac{
        \Gamma\left(\frac{i + 1}{2}\right)
        \Gamma\left(\frac{j + 1}{2}\right)
    }
    {
        \Gamma\left(\frac{i + j + 4}{2}\right)
    }
    %
    \nonumber \\
    %
    K_{i,j} &=
    \frac{
        \Gamma\left(\frac{i + 1}{2}\right)
        \Gamma\left(\frac{j + 4}{2}\right)
    }
    {
        \Gamma\left(\frac{i + j + 5}{2}\right)
    }
    \quad.
\end{proof}
%
Given initial conditions
%
\\[1em]
\begin{minipage}{.33\linewidth}
    \begin{proof}{rT}
        I_{0}(b) &= \frac{\arccos(b) - bb_c}{2}
        %
        \nonumber \\
        %
        I_{1}(b) &= \frac{b_c^3}{3}
        %
        \nonumber
    \end{proof}
\end{minipage}%
\begin{minipage}{.32\linewidth}
    \begin{proof}{rT}
        J_{0,0} &= \pi
        %
        \nonumber \\
        %
        J_{0,1} &= \frac{4}{3}
        %
        \nonumber
    \end{proof}
\end{minipage}%
\begin{minipage}{.33\linewidth}
    \begin{proof}{rT}
        \label{eq:IJK0}
        K_{0,0} &= \frac{4}{3}
        %
        \nonumber \\
        K_{0,1} &= \frac{3\pi}{8}
    \end{proof}
\end{minipage}
\\[1em]
%
we may compute all higher order terms from the recurrence relations
%
\begin{proof}{rT}
    \label{eq:IJKrec}
    I_{j}(b) &= \frac{b^n b_c^3 + (j - 1) I_{j - 2}(b)}{j + 2}
    %
    \nonumber \\
    %
    J_{0,j} &= \left(\frac{j - 1}{j + 2}\right) J_{0,j-2}
    %
    \nonumber \\
    %
    K_{0,j} &= \left(\frac{j + 2}{j + 3}\right) K_{0,j-2}
    %
    \nonumber \\
    %
    J_{i,j} &= \left(\frac{i - 1}{i + j + 2}\right) J_{i-2,j}
    %
    \nonumber \\
    %
    K_{i,j} &= \left(\frac{i - 1}{i + j + 3}\right) K_{i-2,j}
    \quad.
\end{proof}
%
